\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-25 paper.tex
Modify Participants Registration

\maketitle
\section*{\normalsize\textbf{Abstract}}
Transacting IoT data must be different in many from traditional approaches in order to build much-needed trust in data marketplaces—trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experiences, or improve strategic decision-making. In this paper, we propose a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers. This approach can efficiently enhance the degree of transparency, as all contract-oriented interactions will be written on-chain. Storage via an end-to-end encrypted message channel allows transmitting and accessing trusted data streams over distributed ledgers regardless of the size or cost of the device, while simultaneously making a verifiable Auth-compliant request to the platform. Furthermore, the platform will complete matching, trading and refunding processes without human intervention, and it also protects the rights of data providers and consumers through trading policies which apply revolutionary game theory to the machine economy.
\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

@@

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.

Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protection and assurance of data integrity from the source with MAM. Nevertheless, the platform design is centralized, where new devices require manual approval from the IOTA Foundation to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.

@@

\subsection{Participant Registration}
At the beginning, the egistrar creates a registration contract, which maintains all participants' information, including their DID documents and public keys. Anyone can query participants' public keys. Those who would like to sell or purchase data may register to become a data provider or consumer. The registrar has the authority to agree with applications. After that, their identities are available in the registration contract and the launching and trading processes can begin.

>>>>

\maketitle
\section*{\normalsize\textbf{Abstract}}
Transacting IoT data must be different in many from traditional approaches in order to build much-needed trust in data marketplaces—trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experiences, or improve strategic decision-making. In this paper, we propose a decentralized and trustless architecture through the posting of trade records while including the transaction process on distributed ledgers. This approach can efficiently enhance the degree of transparency, as all contract-oriented interactions will be written on-chain. Storage via an end-to-end encrypted message channel allows transmitting and accessing trusted data streams over distributed ledgers regardless of the size or cost of the device, while simultaneously making a verifiable Auth-compliant request to the platform. Furthermore, the platform will complete matching, trading and refunding processes without human intervention, and it also protects the rights of data providers and consumers through trading policies which apply revolutionary game theory to the machine economy.

\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

@@

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided that allows transmission, access, and verification of an encrypted data stream over the Tangle. Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} that not only allows putting data on Tangle without any trusted cloud services, but also allows trading on Tangle where privacy and integrity meet with MAM. Nevertheless, the platform is centralized, where new devices require manual approval from the IOTA Foundation. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.

@@

\subsection{Participant Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys. Everyone can query others' public keys for validation but only registrars have permission to add new members. After registration, the launching and trading processes can begin.
